### 2015-04-06 LaTeX/skewnormal.tex
updated plots for manuscript

$M = 50$ data sets are generated for each design.
For each data set we fit the data using five models
\begin{enumerate} \setlength{\itemsep}{-0.5em}
  \item Gaussian marginal, $K=1$ knots
  \item Skew-$t$ marginal, $K=1$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=1$ knots, $T=q(0.80)$
  \item Skew-$t$ marginal, $K=5$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=5$ knots, $T=q(0.80)$
\end{enumerate}
where $q(0.80)$ is the 80th sample quantile of the data.
The design matrix $\bX$ includes an intercept with a first-order spatial trend with priors of $\beta_\text{int}$, $\beta_\text{lat}$, $\beta_\text{long},  \iid \text{N}(0, 10)$.
The spatial covariance parameters have priors $\log(\nu) \sim \text{N}(-1.2, 1)$, $\gamma \sim \text{Unif}(0, 1)$, $\rho \sim \text{Unif}(15)$.
The skewness parameter has prior $\lambda_2 \sim \text{IG}(0.1, 0.1)$.
The residual variance terms have priors $\sigma^2_t(\bs) \sim \text{IG}(0.1, 0.1)$.
The knots have priors $\bw \sim \text{Unif}(\calD)$.
We do not include skewness for the thresholded models because it cannot be identified with only one tail worth of data, and we do not fit the data using the max-stable methods from \citet{Reich2012} because of the computational constraints.
Each chain of the mcmc ran for 20000 iterations with a burn-in period of 10000 iterations.
Parameters appear to converge properly; however, in the models with multiple partitions (i.e.models 4 and 5) it is hard to assess the convergence of $\bw$, $z(\bs)$, and $\sigma^2(\bs)$ because of partition label switching throughout the MCMC.

@@

\section{Data analysis}\label{s:analysis}
To illustrate this method, we consider the daily maximum 8-hour ozone measurements for July 2005 at 735 Air Quality System (AQS) monitoring sites in the eastern United States as the response (see Figure \ref{fig:ozone}).
For each site, we also have covariate information containing the estimated ozone from the Community Multi-scale Air Quality (CMAQ) modeling system.
Initially, we fit a linear regression assuming a mean function of
\begin{align}
  \bX^T_t(\bs) \bbeta = \beta_0 + \beta_1 \cdot \text{CMAQ}_t(\bs). \label{eq:datamean}
\end{align}
The data from July 10 are shown in Figure \ref{fig:ozone} along with a Q-Q plot of the residuals compared to a skew-$t$ distribution with 10 d.f. and $\alpha = 1$.
\begin{figure}
  \centering
  \includegraphics[width=0.56\linewidth]{plots/ozone-10jul-us.pdf}
  \includegraphics[width=0.41\linewidth]{plots/qq-res.pdf}
  \caption{Ozone values on 10 July 2005 (left) Q-Q plot of the residuals (right)}
  \label{fig:ozone}
\end{figure}
Exploratory data analysis indicates that there is dependence in the high quantile levels of the residuals beyond what we expect in the case if independence.

@@

\subsection{Model comparisons}
We fit the model using Gaussian and skew-$t$ marginal distributions with $K=1, 5, 6, 7, 8, 9, 10, 15$ partitions.
We choose to censor $Y(\bs)$ at $T =$ 0, 50 (0.42 sample quantile), and 75 (0.92 sample quantile) ppb in order to compare results from no, moderate, and high censoring.
The upper threshold of 75 ppb was used because the current air quality standard is based on exceedance of 75 ppb.
As with the simuliation study, for models with a threshold of $T = 75$, we use a symmetric-$t$ marginal distribution.
We also compare models with no time series to models that include the time series.
Finally, as a comparison to max-stable methods, we fit the model using the hierarchical max-stable model of \citet{Reich2012}.
All methods assume the mean function given in (\ref{eq:datamean}).
Each chain of the mcmc ran for 30000 iterations with a burn-in period of 25000 iterations.
Parameters appear to converge properly; however, as before, for models with multiple partitions it is hard to assess the convergence of $\bw$, $z(\bs)$, and $\sigma^2(\bs)$ because of partition label switching throughout the MCMC.
For each model, Brier scores were were averaged over all sites and days to obtain a single Brier score for each dataset.
At a particular threshold or quantile level, the model that fits the best is the one with the lowest score.
We then compute the relative (to Gaussian) Brier scores (see Section \ref{s:simresults}) to compare each model.

@@

We illustrate the predictive capability of our model in Figure \ref{fig:ozoneq99} by plotting the 99th quantile of the posterior predictive density for July in South Carolina and Georgia.
\hl{Include more here about the maps}.

>>>>

$M = 50$ data sets are generated for each design.
For each data set we fit the data using five models
\begin{enumerate} \setlength{\itemsep}{-0.5em}
  \item Gaussian marginal, $K=1$ knots
  \item Skew-$t$ marginal, $K=1$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=1$ knots, $T=q(0.80)$
  \item Skew-$t$ marginal, $K=5$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=5$ knots, $T=q(0.80)$
\end{enumerate}
where $q(0.80)$ is the 80th sample quantile of the data.
The design matrix $\bX$ includes an intercept with a first-order spatial trend with priors of $\beta_\text{int}$, $\beta_\text{lat}$, $\beta_\text{long},  \iid \text{N}(0, 10)$.
The spatial covariance parameters have priors $\log(\nu) \sim \text{N}(-1.2, 1)$, $\gamma \sim \text{Unif}(0, 1)$, $\rho \sim \text{Unif}(15)$.
The skewness parameter has prior $\lambda_2 \sim \text{IG}(0.1, 0.1)$.
The residual variance terms have priors $\sigma^2_t(\bs) \sim \text{IG}(0.1, 0.1)$.
The knots have priors $\bw \sim \text{Unif}(\calD)$.
We do not include skewness for the thresholded models because it cannot be identified with only one tail worth of data, and we do not fit the data using the max-stable methods from \citet{Reich2012} because of the computational constraints.
Each chain of the MCMC ran for 20000 iterations with a burn-in period of 10000 iterations.
Parameters appear to converge properly; however, in the models with multiple partitions (i.e.models 4 and 5) it is hard to assess the convergence of $\bw$, $z(\bs)$, and $\sigma^2(\bs)$ because of partition label switching throughout the MCMC.

@@

\section{Data analysis}\label{s:analysis}
To illustrate this method, we consider the daily maximum 8-hour ozone measurements for July 2005 at 1089 Air Quality System (AQS) monitoring sites in the United States as the response (see Figure \ref{fig:ozone}).
For each site, we also have covariate information containing the estimated ozone from the Community Multi-scale Air Quality (CMAQ) modeling system.
Initially, we fit a linear regression assuming a mean function of
\begin{align}
  \bX^T_t(\bs) \bbeta = \beta_0 + \beta_1 \cdot \text{CMAQ}_t(\bs). \label{eq:datamean}
\end{align}
The data from July 10 are shown in Figure \ref{fig:ozone} along with a Q-Q plot of the residuals compared to a skew-$t$ distribution with 10 d.f. and $\alpha = 1$.
\begin{figure}
  \centering
  \includegraphics[width=0.56\linewidth]{plots/ozone-10jul-us.pdf}
  \includegraphics[width=0.41\linewidth]{plots/qq-res.pdf}
  \caption{Ozone values on 10 July 2005 (left) Q-Q plot of the residuals (right)}
  \label{fig:ozone}
\end{figure}
Exploratory data analysis indicates that there is dependence in the high quantile levels of the residuals beyond what we expect in the case if independence.

@@

\subsection{Model comparisons}
We fit the model using Gaussian and skew-$t$ marginal distributions with $K=1, 5, 6, 7, 8, 9, 10, 15$ partitions.
We choose to censor $Y(\bs)$ at $T =$ 0, 50 (0.42 sample quantile), and 75 (0.92 sample quantile) ppb in order to compare results from no, moderate, and high censoring.
The upper threshold of 75 ppb was used because the current air quality standard is based on exceedance of 75 ppb.
As with the simuliation study, for models with a threshold of $T = 75$, we use a symmetric-$t$ marginal distribution.
We also compare models with no time series to models that include the time series.
Finally, as a comparison to max-stable methods, we fit the model using the hierarchical max-stable model of \citet{Reich2012}.
All methods assume the mean function given in (\ref{eq:datamean}).
To ensure that the max-stable method runs in a reasonable amount of time, we take a stratified sample of the sites to get 800 sites and consider this our new dataset.
We conduct two-fold cross validation using 400 training sites and 400 validation sites as described in Section \ref{s:modelselect}

Each chain of the MCMC ran for 30000 iterations with a burn-in period of 25000 iterations.
Parameters appear to converge properly; however, as before, for models with multiple partitions it is hard to assess the convergence of $\bw$, $z(\bs)$, and $\sigma^2(\bs)$ because of partition label switching throughout the MCMC.
For each model, Brier scores were were averaged over all sites and days to obtain a single Brier score for each dataset.
At a particular threshold or quantile level, the model that fits the best is the one with the lowest score.
We then compute the relative (to Gaussian) Brier scores (see Section \ref{s:simresults}) to compare each model.

@@

We illustrate the predictive capability of our model in Figure \ref{fig:ozoneq99} by plotting the 99th quantile of the posterior predictive density for July in South Carolina and Georgia.
We fit the model using four methods, two reference and two that performed better.
These four methods are
\begin{enumerate}[1.]
  \item Gaussian (reference)
  \item Skew-$t$, $K =$ 1 knot, $T = $ 0, no time series (reference)
  \item Skew-$t$, $K =$ 5 knots, $T = $ 50, no time series (comparison)
  \item Symmetric-$t$, $K =$ 10 knots, $T = $ 75, time series (comparison)
\end{enumerate}
